---
title: "All heatmaps muskoxen"
author: "Nicole Ackermans"
date: "3/14/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Libraries
```{r}
library(readxl)
library(tidyverse)
```

## Imported data
A is 0191, B is 0194, C is 0193
```{r}
Generic0190_pfc<-read_excel("Generic0190_coordinates-all.xlsx")
Generic0193_pfc<-read_excel("Generic0193_coordinates-all.xlsx")
Generic0194_pfc<-read_excel("Generic0194_coordinates-all.xlsx")
Generic0190_parietal<-read_excel("Generic0190parietal_coordinates.xlsx")
Generic0193_parietal<-read_excel("Generic0193parietal_coordinates.xlsx")
Generic0194_parietal<-read_excel("Generic0194parietal_coordinates.xlsx")

Generic0190_pfc <- Generic0190_pfc %>%
  mutate(group = "A")

Generic0193_pfc <- Generic0193_pfc %>%
  mutate(group = "B")

Generic0194_pfc <- Generic0194_pfc %>%
  mutate(group = "C")

Generic0190_parietal <- Generic0190_parietal %>%
  mutate(group = "D")

Generic0193_parietal <- Generic0193_parietal %>%
  mutate(group = "E")

Generic0194_parietal <- Generic0194_parietal %>%
  mutate(group = "F")

my_data <- rbind(Generic0190_pfc, Generic0193_pfc, Generic0194_pfc, Generic0190_parietal, Generic0193_parietal, Generic0194_parietal)
```

# Assign datasets
```{r}
Generic0190_pfc <- Generic0190_pfc %>%
  mutate(group = "A")

Generic0193_pfc <- Generic0193_pfc %>%
  mutate(group = "B")

Generic0194_pfc <- Generic0194_pfc %>%
  mutate(group = "C")

Generic0190_parietal <- Generic0190_parietal %>%
  mutate(group = "D")

Generic0193_parietal <- Generic0193_parietal %>%
  mutate(group = "E")

Generic0194_parietal <- Generic0194_parietal %>%
  mutate(group = "F")
```

#Correction to translate to same point of origin
#0190_xnew = x0190 - x0913
#0910_ynew = y0910 + y0913
"0190_x" <- -25638.20 - -1018.86
"0190_y" <- -8097.15 + -2581.53

#0194_xnew = x0194 - x0193
#0194_ynew = y0194 - y0913
"0194_x" <- -63270.14 - -1018.86	
"0194_y" <- -4712.48 - -2581.53
```{r}
my_data %>%
  group_by(group) %>%
  summarize(min_x = min(x),
            min_y = min(y))

"0190_x" <- -25638.20 - -63270.14
"0190_y" <- -4712.48 + -8097.15

"0194_x" <- -1018.86 - -63270.14	
"0194_y" <- -2581.53 - -4712.48

my_data_transform <- my_data %>%
  mutate(new_x = ifelse(group == "B", paste(x), 
                        ifelse(group == "A", x - `0190_x`,
                               ifelse(group == "C", x - `0194_x`, NA
                                      ))),
         new_y = ifelse(group == "B", paste(y), 
                        ifelse(group == "A", y + `0190_y`,
                               ifelse(group == "C", y - `0194_y`, NA
                                      )))) %>%
  mutate(new_x = as.numeric(new_x),
         new_y = as.numeric(new_y))

my_data_transform
```

# Min and Max for scale
```{r}
min(my_data_transform$new_x)

max(my_data_transform$new_x)

min(my_data_transform$new_y)

max(my_data_transform$new_y)
```


```{r, fig.width = 7, fig.height=15}
my_data_transform %>%
  group_by(group) %>%
  count()

labels <- data.frame(
  group = c("A", "B", "C"),
  label = c("n = 2621", "n = 5465", "n = 25446")
)

my_data_transform %>%
  ggplot(aes(x = new_x, y = new_y)) +
  stat_density_2d(aes(fill=..level..), geom="polygon", bins=10)+
  scale_fill_viridis_c(option = "viridis", alpha=0.7)+ 
  scale_x_continuous(limits = c(-64000, -8020)) +
  scale_y_continuous(limits = c(-25000, 29000)) +
  facet_wrap(~ group, ncol = 1) +
  geom_text(data = labels, aes(x = -20000, y = 25000, label = label, group = group)) +
  theme_classic() +
  theme(strip.background = element_blank())

#ggsave("MuskoxPFC_heatmaps_220312.png", plot=AllHeatmaps, dpi=300)
```

